Flaring star-planet interactions in star-planet systems in Kepler and TESS

### 2023-05-12 src/tex/ms.tex
[showyourwork] overleaf sync

\subsection{Tidal vs. magnetic flaring star planet interaction}

@@

Among the systems, HIP 67522 appears with tentative signs of both tidal and magnetic interaction (measured and expected in the different scenarios). On the one hand, since the flares in HIP 67522 mostly appear close to the transit phase, and not during eclipse, this may favor magnetic interaction, and the tidal signal would only be an artifact. On the other hand, the narrow range in which most of the flares on HIP 67522 occurred might favor a well-located tidal bulge. It is conceivable that both effects play a role at the same time.

KOI-12, which lacks signal with $P_{orb}$ despite high expected power of magnetic interaction, shows elevated expected and measured tidal interaction. This could be interpreted as KOI-12 b orbiting outside the Alfv\'en radius, unable to interact magnetically, but tidally. We note that KOI may be evolving off the main sequence, so that the tidal interaction estimates might not be accurate for this star. TAP 26, which shows no signs of magnetic SPI, does not show any sign of tidal interaction despite both being high as expected from models. This could again be due to the inclination of TAP 26's orbit, but only if the flares caused by the tidal bulge are not too close to the equator. In that case, TAP 26's tidally induced flares should be more modulated than the magnetically induced ones.

Kepler-42 is neither expected to interact magnetically, nor did it show any deviation from random flare timing in phase with $P_{orb}$. However, since it is the system with the shortest planetary orbit in our sample, it is both expected to and does show marginal signal of tidal interaction. Kepler-42 is very similar to TOI-540, which also is a small M dwarf with a likely terrestrial planet in a very short orbit. The key difference may be that Kepler-42 is rotating at about 70 days, and therefore expected to have a relatively weak magnetic field, whereas TOI-540 is a young star with a rotation period $<1\,$d. TOI-540 is expected to have lower tidal interaction strength than Kepler-42 due to TOI-540 b's wider orbit, and also shows a weaker tidal SPI signal in all three scenarios. K2-25 and AU Mic are similar, but differ from TOI-540 -- both show tentative signs of magnetic SPI, but are consistent within $1\sigma$ with no observable tidal interaction.

>>>>

\subsubsection{Tidal vs. magnetic flaring star planet interaction}

@@

\paragraph{HIP 67522} appears with tentative signs of both tidal and magnetic interaction (measured and expected in the different scenarios). On the one hand, since the flares in HIP 67522 mostly appear close to the transit phase, and not during eclipse, this may favor magnetic interaction, and the tidal signal would only be an artifact. On the other hand, the narrow range in which most of the flares on HIP 67522 occurred might favor a well-located tidal bulge. Conceivably, both effects play a role at the same time.

\paragraph{KOI-12}, which lacks signal with $P_{orb}$ despite high expected power of magnetic interaction, shows elevated expected and measured tidal interaction. This could be interpreted as KOI-12 b orbiting outside the Alfv\'en radius, unable to interact magnetically, but tidally. We note that KOI may be evolving off the main sequence, so that the tidal interaction estimates might not be accurate for this star.

\paragraph{TAP 26,} which shows no signs of magnetic SPI, does not show any sign of tidal interaction despite both being high according to the scaling laws. This could again be due to the inclination of TAP 26's orbit, but only if the flares caused by the tidal bulge are not close to the equator. Otherwise, TAP 26's tidally induced flares should be more modulated than the magnetically induced ones.

\paragraph{Kepler-42 and TOI-540}. Kepler-42 is neither expected to interact magnetically, nor did it show any deviation from random flare timing in phase with $P_{orb}$. However, since it is the system with the shortest planetary orbit in our sample, it is both expected to and does show marginal signal of tidal interaction. Kepler-42 is very similar to TOI-540, which also is a small M dwarf with a likely terrestrial planet in a very short orbit. A key difference is that Kepler-42 is rotating at about 70 days, and therefore expected to have a relatively weak magnetic field, whereas TOI-540 is a young star with a rotation period $<1\,$d. TOI-540 is expected to have lower tidal interaction strength than Kepler-42 due to TOI-540 b's wider orbit, and also shows a weaker tidal flaring SPI signal in all three scenarios. K2-25 and AU Mic are similar, but differ from TOI-540 -- both show tentative signs of magnetic SPI, but are consistent within $1\sigma$ with no observable tidal interaction.
